HAMdetector: A Bayesian regression model that integrates information to detect HLA-associated mutations

### 2021-02-16 docs/main.tex
add genes to dataset list
starting epitope section of methods

We chose a logistic regression model as a backbone because it is easily extensible, and because coefficients can be interpreted in the familiar way as summands on the log-odds scale.

@@

\textit{Binding affinity prediction}

\hl{DaHo: Mein Verständnis von Materials and Methods ist, dass hier die Methoden aufgeführt werden, z.B. die Methoden für die Berechnung von Affinitäten, siehe z.B. https://academic.oup.com/bioinformatics/article/36/21/5159/5874440}

>>>>

We chose a logistic regression model as backbone because it is easily extensible, and because coefficients can be interpreted in the familiar way as summands on the log-odds scale.

@@

\subsubsection{Inclusion of CTL epitope predictions}

%A major CTL escape mechanism is the generation of mutations in viral peptides that prevent peptide presentation by MHC I to T cell receptors. 
Mutations in CTL epitopes (the viral peptides that are presented by MHC I molecules to T cell receptors) can prevent or worsen epitope presentation to CTLs and thus cause viral CTL escape. Therefore, mutations in epitopes are prime candidates for CTL escape. This means that the fact of a replacement

A major mechanism for viral CTL escape is the generation of
